### 2021-07-08 rad-icfp-2021/correctness.tex

We can interpret Source in $\CSource$ as follows.
TODO

\begin{proposition}[construction above gives UNF]
    TODO
\end{proposition}

@@

This allows to form a concategory $\CTarget$ from the syntactic multicategory for Target.
We can interpret $\ConcatT$ in $\CTarget$ as follows.
TODO

This interpretation is in essence $\UNFSymbol^{-1}$. 
The difference is that to preserve typing, the semantic $\UNFSymbol^{-1}$
sends a non Jacobian primitive to a tuple, as in the example \ref{}. 
This is highly inefficient and the the syntactic $\UNFSymbol^{-1}$ 
additionally projects to the last element, where the non trivial information of the term is.

@@

\begin{definition}[$\Dsynrevsymbol_{\rho}$ as a lax functor]
    We define $\Dsynrevsymbol_{\rho}:\ConcatS\to\ConcatT$ as follows.
    $\Dsynrevsymbol_{\rho}$(![A$_1$,$\ldots$,A$_n$])=[A$_1$,$\ldots$,A$_n$,A$_1\times\ldots\times$A$_n\to \rho$]!.
\end{definition}

>>>>

We can interpret Source in $\CSource$ as follows. The functor is an identity on types. 
On morphisms, we interpret them as morphisms in the concategory as follows.
The terminal map is interpreted as the identity. The operators !op1,op2! by themselves.
Crucially, the semantics of a !let! becomes composition in the concategory. 
The semantics of a variable is the pairing of the identity with a projection.
The operation !map2 (x,y.e)! is interpreted as the pairing of the identity and itself, and !reduce (x,y.e$_1$) $e_2$! as itself.

Interpretating Source in $\CSource$ allows us to see terms of Source as morphisms in the concategory $\ConcatS$.
This allows us to compare to semantics of terms of Source and of Source UNF.
The following proposition can be shown by induction on the structure of the terms.

\begin{proposition}[construction above gives UNF]
    Let !$\Gamma \vdash$ e:A! be a term in Source. 
    Seen as morphisms in $\CSource$, we have !$\seml$e$\semr$=$\seml\UNFSymbol$(e)$\semr$!.
\end{proposition}

@@

This allows to form a concategory $\CTarget$ from the syntactic multicategory for Target.
We can interpret $\ConcatT$ in $\CTarget$. 
The functor is identity on objects, sends operations !op1,op2! to themselves. 
It sends Jacobian operations to terms of Target as given by $\UNFSymbol^{-1}$ in Figure~\ref{fig:unf_to_target}

This interpretation is in essence $\UNFSymbol^{-1}$. 
The difference is that to preserve typing, the semantic $\UNFSymbol^{-1}$
sends a non Jacobian primitive to a tuple, as in the Example \ref{exm:unf}. 
This is highly inefficient and the the syntactic $\UNFSymbol^{-1}$ 
additionally projects to the last element, where the non trivial information of the term is.

@@

\begin{definition}[$\Dsynrevsymbol_{\rho}$ as a lax functor]
    We define $\Dsynrevsymbol_{\rho}:\ConcatS\to\ConcatT$ as follows.
    $\Dsynrevsymbol_{\rho}$(![A$_1$,$\ldots$,A$_n$])=[A$_1$,$\ldots$,A$_n$,A$_1\times\ldots\times$A$_n\to \rho$]!.
    TODO
\end{definition}
